Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-10 main_paper.tex
update the tables in application section
Only the CIs changed a little bit, the text in this section does not
explicitly quote any CIs.

For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K(X_{i}/h).
\end{align*}

Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) = \V(\hat\tau(h) \mid X_{1},\dots,X_{n}),
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid X_1,\dots,X_n) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix. The plug-in bias-corrected
estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}^{bc}(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  \frac{\hat{\tau}^{bc}(h, b) - \tau}{V^{bc}(h, b)^{1/2}} \to^d N(0,1)
\end{equation*}
with $V^{bc}(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term.\footnote{%
  $C(h,b)$ and $V(h)$ are defined precisely in the mathematical appendix.} %
This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples even when the naive interval performs badly.

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
\end{theorem}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and
  Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate $\hat g(\cdot)$
    and the residuals $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{bc*}(h,b), \dots, \hat\tau_{B_{2}}^{bc*}(h,b)$. For the
    $k$th replication:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
      \end{align*}
      for all $i = 1,\dots,n$.
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$
      for weights:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{-,h}(X_{i}), \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{+,h}(X_{i}).
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
      $(Y_1^*,\, X_1),\dots,(Y_n^*,\, X_n)$ set using the same bandwidths
      $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{bc*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
    $\hat\tau_1^{bc*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{bc*}(h,b) - \tau^*$
    as the sampling distribution of $\hat \tau^{bc} - \tau$.
  \end{enumerate}
\end{algorithm}

One brief remark on implementing these algorithms. Many of the matrix operations
required to estimate the local polynomials only involve the regressors and,
therefore, only need to be computed once. For example, the parameter estimates
for the linear model on the treated group are equal to
\[
\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
\]
where
\begin{align*}
\mathbf{X} &= \begin{pmatrix*} 1 & X_1 \\ 1 & X_2 \\ \vdots & \vdots \\ 1 & X_n \end{pmatrix*} &
\mathbf{Y} &= \begin{pmatrix*} Y_1 \\ Y_2 \\ \vdots \\ Y_n \end{pmatrix*} &
\mathbf{K}_+ &= \begin{pmatrix*}
  K_{+,h}(X_1) & 0 & \cdots & 0 \\
  0 & K_{+,h}(X_2) & \cdots & 0 \\
  0 & 0 & \ddots & 0 \\
  0 & 0 & \cdots & K_{+,h}(X_n) \end{pmatrix*}.
\end{align*}
The matrix $\mathbf{W}_{+,1}$ is not affected by the bootstrap so it can be
computed once initially and reused in the bootstrap calculations and each
bootstrap replication just requires a single matrix-vector multiplication. The
other parameter estimates have this property as well. Consequently, the
computational burden of this iterated bootstrap is much lower than might
appear.\footnote{%
  An open-source implementation of this algorithm written in R, which was used
  for the empirical and Monte Carlo components of this paper, is available
  online at \url{https://github.com/grayclhn/boot-rd}.} %

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{equation*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V^{bc}(h,b) \to^p 1
  \end{equation*}
  and
  \begin{multline*}
    \sup_{x,\tau}
    \Big\rvert \Pr^*\big[ \sqrt{nh}
    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
    - \Pr\big[ \sqrt{nh}
    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
  \end{multline*}
\end{theorem}

@@

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to those obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained are comparable to the analytical
alternative, albeit with slightly lower coverage and shorter
length of the intervals in the specifications implemented. We also find that
all of the bias corrected methods can offer substantial improvements over
estimators that do not bias correct.

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
comparable with theirs and with the rest of the literature. While they use this experimental design with homoskedastic errors, we introduce heteroskedasticity following the design in \cite{mackinnon2013thirty}. We control the degree of heteroskedasticity through the parameter $\gamma$ and a function $z(\gamma)$. When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT. When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined. For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.

\nocite{lee2008rand}%
The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
congressional elections. Lee estimates the incumbency advantage in electoral
races for the House of Representatives --- parties that received the largest
vote share in the previous election are the incumbents, which creates the
discontinuity. The conditional expectation is a fifth order polynomial fit to
that dataset, (after excluding a small number of extreme observations; see
\citealp{IK}, or CCT for further details) giving
\begin{equation*}
  \mu_{1}(x) =
  \begin{cases}
    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
    & \textif\ x < 0 \\
    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
    & \otherwise.
  \end{cases}
\end{equation*}
The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
results for the analytically-corrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each approach.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.
In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart. In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity. 
The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.

These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and similarly well compared to the analytical bias correction procedures proposed
by CCT.

@@

In 1965, the Head Start program was established to help poor children aged three
to five and their families. The program elements include parent involvement,
nutrition, social services, mental health services and health services. To
promote this program in the most needing area, the Office of Economic
Opportunity provided grant-writing assistance to the poorest 300 counties in the
United States based on the 1960 poverty rate. So the poverty rate of the 300th
poorest county serves as a sharp cutoff of treatment. It is shown in
\cite{ludwig2007} that the 228 ``treatment'' counties with poverty rates 10
percentage points above this cutoff have average Head Start spending per
four-year-old as twice of that for 349 ``control'' counties with poverty rates
10 percentage points below this cutoff.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                      & ATE     & \multicolumn{2}{r}{95\% CI}            &     &  $h$ &   $b$ & p-value \\
    \midrule
    LM (2007)         & --1.895 & (--3.930                    & 0.139)   & 9   &      &       & 0.036 \\
    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18  &      &       & 0.081 \\
    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
    CCT               & --3.795 & (--7.040                    & --0.551) & 3   & .888 & 6.807 &       \\ 
    Wild bootstrap    & --3.800 & (--6.738                    & --0.450) & 3   & .888 & 6.807 &       \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on mortality. The first three
    rows come from Table 3 in \cite{ludwig2007} except ``95\% CI,'' which is
    calculated using the conventional asymptotic interval estimator.
    The last two rows list results from two robust procedures.}
  \label{tbl:2}
\end{table}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                   & ATE   & \multicolumn{2}{r}{95\% CI} & & $h$     & $b$ & p-value     \\
    \midrule                                                                          \\
    \multicolumn{5}{l}{Fraction ``high school or more'' (Panel A)}                    \\
    \midrule
    LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
    CCT            & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
    Wild bootstrap & 0.055 & (0.010                      & 0.096) & 3&.671 & 8.618       \\\\
    \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
    \midrule
    LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
    CCT            & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
    Wild bootstrap & 0.052 & (0.007                      & 0.091) & 5&.076 & 10.251      \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on education for cohort
    18--24 in 1990. Panel A uses the fraction of people with high school
    or more as dependent variable. Panel B uses the fraction of people
    with some college or more as dependent variable. The first row in
    each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI,''
    which is calculated using the conventional asymptotic interval estimator.
    The last two rows in
    each panel list results from two robust procedures.}
  \label{tbl:3}
\end{table}

>>>>

For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
\begin{equation*}
  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
\end{equation*}
with
\begin{align*}
  \hat {\mu}_{+}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
\intertext{and}
  \hat {\mu}_{-}(h)
  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K_{h}(X_{i}/h).
\end{align*}

Conventional (naive) confidence intervals can be calculated by using an
asymptotic approximation for $\hat\tau(h)$. In particular, if
\begin{gather}
  \label{eq:1}
  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
  \intertext{with}
  \notag
  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
\end{gather}
then valid confidence intervals can be constructed through the usual method of
inverting the $t$-test.\footnote{%
  The mathematical appendix of this paper gives a precise definition for
  $V(h)$.} %
This procedure gives the widely-used interval estimator
\begin{equation*}
  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
\end{equation*}
where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
distribution.

@@

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid X_1,\dots,X_n) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix. The plug-in bias-corrected
estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}} \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term.\footnote{%
  $C(h,b)$ and $V(h)$ are defined precisely in the mathematical appendix.} %
This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples even when the naive interval performs badly.

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:4}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
  \to^{d} N(0,1),
\end{equation}
where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
\end{theorem}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define the same notation as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate $\hat g(\cdot)$
    and the residuals $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
  \item Repeat the following steps $B_{2}$ times to produce the
    bootstrap estimates
    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
    $k$th value:
    \begin{enumerate}
    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
      and bounded fourth moments independent of the original data and
      construct
      \begin{align*}
        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
        \intertext{and}
        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}) \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}).
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
      using the same bandwidths $h$ and $b$ that are used in the rest of this
      algorithm but reestimating all of the local polynomials on the bootstrap
      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
      represent the bias estimator returned by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
      - \Delta^{**}(h,b)$.
    \end{enumerate}
  \item Use the empirical CDF of
    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
    construct confidence intervals, etc.
  \end{enumerate}
\end{algorithm}

@@

\begin{theorem}\label{T2}
  Under Assumptions~\ref{A1} and~\ref{A2},
  \begin{gather*}
    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
  \intertext{and}
    \sup_{x}
    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
  \end{gather*}
\end{theorem}

@@

\section{Simulation Evidence}\label{sim}

This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals similar to those obtained by the analytical procedures established
in CCT. The bootstrap CIs obtained compare favorably to the analytical
alternative, with coverage slightly closer to nominal coverage and shorter
length of the intervals in the specifications implemented. We also find that
all of the bias corrected methods can offer substantial improvements over
estimators that do not bias correct, including a ``naive'' bootstrap procedure.

The Monte Carlo experiments have a similar structure. For all of them, we
generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ will index the specific DGP. This is the experimental design used by
\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
comparable with theirs and with the rest of the literature. They use this experimental design with a constant $\sigma_i = 0.1295$. We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity. When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT. When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.
\footnote{The rescaling requires that $\max(h, b)$ is known, which is usually not the case in practice because $h$ and $b$ are data-driven. For simplicity, we firstly find $\overline{\max[h, b]}$ from \textbf{homoskedastic} data through 500 replications and then calculate $z(\gamma)$ for every bootstrap data accordingly. In our simulation, $\overline{\max[h, b]}$ is obtained by (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector and (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$. Once $\overline{\max[h, b]}$ is known, we use it to generate heteroskedastic data using following steps: (1) generate random running variable $X_i$, (2) let $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$ and calculate the standard deviation and (3) generate disturbance term and outcome $Y_i$ accordingly.} 
We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.

\nocite{lee2008rand}%
The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
congressional elections. Lee estimates the incumbency advantage in electoral
races for the House of Representatives --- candidates who received the largest
vote share in the previous election are the incumbents, which creates the
discontinuity. The conditional expectation is a fifth order polynomial fit to
that dataset, (after excluding a small number of extreme observations; see
\citealp{IK}, or CCT for further details) giving
\begin{equation*}
  \mu_{1}(x) =
  \begin{cases}
    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
    & \textif\ x < 0 \\
    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
    & \otherwise.
  \end{cases}
\end{equation*}
The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.

@@

Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
results for the analytically-corrected interval. The first three columns give the bias,
standard deviation, and Root-MSE of the point
estimators corresponding to each confidence interval.  As expected, both
bias corrected estimators have
bias close to zero, with their standard deviation largely
determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
bootstrap and analytically-corrected estimators have essentially the same
standard deviation across all of the DGPs.

The column ``CI Coverage'' lists the experimental coverage of each interval.
In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart. In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity. 
The final column, ``CI Length,'' 
indicates that our proposed bootstrap procedure consistently generates narrower intervals.

These are DGPs where the naive confidence intervals are known to perform poorly,
and this set of simulation results indicates that our proposed bootstrap approach
is quite competitive with analytical methods for producing valid intervals.
Overall, the bootstrap bias-correction procedure proposed in this paper provides
a simple alternative to obtain valid robust confidence intervals in RD designs
and performs well compared to the analytical bias correction procedures proposed
by CCT.

@@

In 1965, the Head Start program was established to help poor children age three
to five and their families. The program elements include parent involvement,
nutrition, social services, mental health services and health services. To
promote this program in the most needing area, the Office of Economic
Opportunity provided grant-writing assistance to the poorest 300 counties in the
United States based on the 1960 poverty rate. So the poverty rate of the 300th
poorest county serves as a sharp cutoff of treatment. It is shown in
\cite{ludwig2007} that the 228 ``treatment'' counties with poverty rates 10
percentage points above this cutoff have average Head Start spending per
four-year-old as twice of that for 349 ``control'' counties with poverty rates
10 percentage points below this cutoff.

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                      & ATE     & \multicolumn{2}{r}{95\% CI}            &     &  $h$ &   $b$ & p-value \\
    \midrule
    LM (2007)         & --1.895 & (--3.930                    & 0.139)   & 9   &      &       & 0.036 \\
    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18  &      &       & 0.081 \\
    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
    CCT               & --3.795 & (--6.885                    & --0.706) & 3   & .888 & 6.807 &       \\ 
    Wild bootstrap    & --3.800 & (--6.781                    & --0.408) & 3   & .888 & 6.807 &       \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on mortality. The first three
    rows come from Table 3 in \cite{ludwig2007} except ``95\% CI,'' which is
    calculated using the conventional asymptotic interval estimator.
    The last two rows list results from two robust procedures.}
  \label{tbl:2}
\end{table}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{lrr@{, }rr@{}rrr}
    \toprule
                   & ATE   & \multicolumn{2}{r}{95\% CI} & & $h$     & $b$ & p-value     \\
    \midrule                                                                          \\
    \multicolumn{5}{l}{Fraction ``high school or more'' (Panel A)}                    \\
    \midrule
    LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
    CCT            & 0.055 & (0.013                      & 0.097) & 3&.671 & 8.618       \\
    Wild bootstrap & 0.055 & (0.010                      & 0.097) & 3&.671 & 8.618       \\\\
    \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
    \midrule
    LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
    CCT            & 0.051 & (0.006                      & 0.096) & 5&.076 & 10.251      \\
    Wild bootstrap & 0.052 & (0.006                      & 0.092) & 5&.076 & 10.251      \\
    \bottomrule
  \end{tabular}
  \caption{The effect of Head Start assistance on education for cohort
    18--24 in 1990. Panel A uses the fraction of people with high school
    or more as dependent variable. Panel B uses the fraction of people
    with some college or more as dependent variable. The first row in
    each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI,''
    which is calculated using the conventional asymptotic interval estimator.
    The last two rows in
    each panel list results from two robust procedures.}
  \label{tbl:3}
\end{table}
